\section{The Demo Description Language}

current version is 1.0

\subsection{Introduction}
The Demo Description Language (DDL) is a textual description of a IPOL demo that 
allows to compile, generate a web interface, and run a demo. The description is 
written in JSON (JavaScript Object Notation) format, which is a standard format 
used in web applications. Current the JSON files are located in the 'static/JSON'
subdirectory. This language is evolving to allow a maximum number 
of demos to be described without the need to manually write HTML or Python code 
for a given demo. Each main key in the description file is described in the 
following sections:
\begin{itemize}
  \item \textit{general}: some general options;
  \item \textit{build}: everything needed to download and compile the source code;
  \item \textit{inputs}: description of the different inputs;
  \item \textit{params}: description of the parameters, for the param page;
  \item \textit{run}: commands to run the demo;
  \item \textit{config}: configuration, saving demo information;
  \item \textit{archive}: describes what is saved in archive when inputs are uploaded;
  \item \textit{results}: displaying the result page.
\end{itemize}



{\bf Note:} in JSON format, always use double quotes around keys or string 
values, not single quotes. Use can use the following link (or any other validator)
to check if your JSON code is valid: http://jsonlint.com/.
Also be carreful with commas, missing or additional commas are often the cause of
invalid JSON files.

\ToDo{[Miguel]: Why JSON? XML seems more readable. [Karl] I don't agree, for me
XML is more cumbersome, but JSON has the problem of not accepting comments, they 
are different ways to get around it. Jsonnet seems to be a nice option.}

%-------------------------------------------------------------------------------
\subsection{The \emph{general} section}
The general section describes global information about the demo.
It is a set of  (key,value) pairs, described in the following table.
Many keys are derived from the static variables of the previous 'app' Python class.\\
% 
\begin{longtable}{|>{\bf}L{\dimexpr 0.28\linewidth}|L{\dimexpr 
0.57\linewidth}|c|}
\hline
 \centering {key}     & \centering {\bf description} & {\bf req} 
\tabularnewline \hline \hline
 demo\_title         & demo title & yes\\ \hline
 input\_description  & description at the top of the input selection page, 
                      contains html as a single string or as an array of string
                      that will be concatenated and separated with spaces.
                     & yes \\ \hline
 param\_description  & description at the top of the para\-meters page,
                      contains html as a single string or as an array of string
                      that will be concatenated and separated with spaces.
                      & yes
                      \\ \hline
 is\_test           & boolean (true/false), if true will be removed from demos 
if the server is in production mode.& yes  \\ \hline
 xlink\_article     & defines the link to the article webpage & yes  \\ \hline
 enable\_crop       & enable or disable cropping for this demo, default is true 
                      (crop enabled). & no   \\ \hline
 crop\_maxsize      & limit allowed crop size in both width and height, the string
                      can contain an Angular expression which will be evaluated & no \\ \hline
 thumbnail\_size    & set initial thumbnail size for the input selection page & no \\ \hline
 input\_condition   & sets a condition on inputs using for example the input sizes & no \\ \hline
 show\_results\_on\-\_error & show results even if the demo returned a run-time error.
                    the demo will be able to display pertinent information & no \\ \hline
\caption{Keys for the 'general' section ({\em req} means required).}
\end{longtable}

%-------------------------------------------------------------------------------
\subsection{The \emph{build} section}

The build section contains an array of build descriptions in the form
''[ \{...\}, \{...\}, ...] ''. For each description, an archive containing the 
source code is downloaded and compiled using either 'make' or 'cmake' features.
It has the following information:

\subsubsection{\emph{make} type}

\begin{longtable}{|>{\bf}L{\dimexpr 0.25\linewidth}|L{\dimexpr 0.6\linewidth}|c|}
\hline
\centering {key}     & \centering {\bf description} & {\bf req} \tabularnewline 
\hline \hline
 build\_type    & make & yes \\ \hline
 url        & full url link to download the demo source code & yes \\ \hline
 srcdir     & subdirectory from the extracted archive where the source code is 
            located & yes \\ \hline
 prepare\_make & shell command used to fix compilation errors of the source code,
                since the source code is steady & no  \\ \hline
 binaries   & list of binaries and their associated paths relative to the source 
            code path. In case of 'make' build type, the first path is the compilation
            path, where the make command is called, the second path is the binary
            path. You can run make without a binary name by setting the second
            path to a directory, then all files from this directory will be copied
            to the demo binary path.
            & yes \\ \hline
 flags      & make command compilation flags & yes \\ \hline
 scripts    & list of scripts and their associated paths relative to the source 
            code path & no  \\ \hline
\caption{Keys for the 'make' type.}
\end{longtable}

\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
"build": [ { 
  "build_type" : "make",
  "url"        : "http://www.ipol.im/xxx/ldm_q1p.zip", 
  "srcdir"     : ".",
  "binaries"   : [ [".","lens_distortion_correction"] ],
  "flags"      : "OMP=1 -j4" } ]
\end{lstlisting}

\subsubsection{\emph{cmake} type}

\begin{longtable}{|>{\bf}L{\dimexpr 0.25\linewidth}|L{\dimexpr 0.6\linewidth}|c|}
\hline
\centering {key}     & \centering {\bf description} & {\bf req} \tabularnewline 
\hline \hline
 build\_type  & cmake & yes \\ \hline
 url          & same as make type & yes \\ \hline
 srcdir       & same as make type & yes \\ \hline
 prepare\_cmake & shell command used to fix compilation errors of the source code,
                since the source code is steady & no  \\ \hline
 cmake\_flags  & cmake flags for configuration ('Release' build type is 
                automatically set) & no  \\ \hline
 binaries   &  same as make type& yes \\ \hline
 flags      &  same as make type & yes \\ \hline
 scripts    & same as make type & no  \\ \hline
\caption{Keys for the 'cmake' type.}
\end{longtable}

\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
"build": [ { 
  "build_type" : "cmake",
  "url"        : "http://www.ipol.im/xxx/ldm_q1p.zip", 
  "srcdir"     : ".",
  "binaries"   : [ [".","lens_distortion_correction"] ],
  "flags"      : "OMP=1 -j4" } ]
\end{lstlisting}

%-------------------------------------------------------------------------------
\subsection{The \emph{inputs} section}
The inputs section describes the set of input data of the algorithm (images, 
videos, flows, etc..).

\subsubsection{\emph{image} type}

\begin{longtable}{|>{\bf}L{\dimexpr 0.17\linewidth}|L{\dimexpr 0.68\linewidth}|c|}
\hline
\centering {key}     & \centering {\bf description} & {\bf req} \tabularnewline 
\hline \hline
 type         & image & yes \\ \hline
 description  & Short name or description of the input, it will used to display 
the input as the label inside the 'gallery' html display & yes \\ \hline
 max\_pixels   &  sets the maximal number of pixels of the input image, 
bigger images will be downsized, if 0 no resizing is done. The resizing as 
defined in the image class uses python PIL resizing with 'antialias' option. 
Input can be a number or a string that will be evaluated in Angular.  & .. \\ \hline
 max\_weight   & max size (in bytes) of an input file, prevents uploading 
bigger files. Input can be a number or a string that will be evaluated in Angular. & .. \\ \hline
 dtype        & input image expected data type, used as parameter of 
image.convert() method. Possible values are '1x8i' and '3x8i' which are 
converted respectively to 'L' and 'RGB' for PIL. & .. \\ \hline
 ext          & input image expected extention (ie. file format) & .. \\ \hline
\caption{Keys for the 'text\_file' type.}
\end{longtable}

\subsubsection{\emph{flow} type}

\ToDo{[Karl]: explain how to assiocate an image to represent the flow. }


\begin{longtable}{|>{\bf}L{\dimexpr 0.17\linewidth}|L{\dimexpr 0.68\linewidth}|c|}
\hline
\centering {key}     & \centering {\bf description} & {\bf req} \tabularnewline 
\hline \hline
 type             & flow & yes \\ \hline
 description      & same as image & yes \\ \hline
 max\_pixels      & same as image & yes \\ \hline
 max\_weight      & same as image & yes \\ \hline
 dtype            & same as image & yes \\ \hline
 ext              & same as image & yes \\ \hline
 required         & boolean: tells if the flow is required for the algorithm
or optional, default is optional. For example, the ground truth may be optional.& no \\ \hline
\caption{Keys for the 'text\_file' type.}
\end{longtable}


%-------------------------------------------------------------------------------
\subsection{The \emph{params} section}
The params section describes the set of parameters needed by a demo, their 
constraints and their visual appearance. It is defined as an array of sets, 
where each set contains (key,value) pairs.


\subsubsection{ \emph{range} type}

The values of the range type are stored as numbers, so no double quotes are 
required around the values. The default value is stored with the 'values' field.

\begin{longtable}{|>{\bf}L{\dimexpr 0.15\linewidth}|L{\dimexpr 
0.7\linewidth}|c|}
\hline
 \centering {key}     & \centering {\bf description} & {\bf req} 
\tabularnewline \hline \hline
 type  & range       & yes \\ \hline
 id     & parameter name in lowercase letters  & yes \\ \hline
 label & description of the parameter or contents if type is label. & yes
                      \\ \hline
 values & set min,max,step and default values using the following key/value 
scheme \{ 'min':val, 'max':val, 'step':val, 'default':val \} & yes
                      \\ \hline
\caption{Keys for the 'range' type.}
\end{longtable}


\subsubsection{ \emph{selection\_collapsed} type}

The values of the selection are stored as strings, so we map each label with a 
string value. The default value is stored in a separate field.

\begin{longtable}{|>{\bf}L{\dimexpr 0.25\linewidth}|L{\dimexpr 
0.6\linewidth}|c|}
\hline
 \centering {key}     & \centering {\bf description} & {\bf req} 
\tabularnewline \hline \hline
 type  & selection\_collapsed    & yes \\ \hline
 id     & parameter name in lowercase letters & yes \\ \hline
 label & description of the parameter. & yes
                      \\ \hline
 values & set of (key,value) pairs, where the key is the displayed text and the 
value a string representing the corresponding value, for example \{ 
'black':'0', '1\%':'0.01' \} & yes
                      \\ \hline
 default\_value & defines the default value for this parameter, should be one 
the values defined in 'values'. & yes \\ \hline
\caption{Keys for the 'selection\_collapsed' type.}
\end{longtable}

\subsubsection{ \emph{label} type}

The label  can be used as a title to separate groups of parameters.

\begin{longtable}{|>{\bf}L{\dimexpr 0.27\linewidth}|L{\dimexpr 
0.58\linewidth}|c|}
\hline
 \centering {key}     & \centering {\bf description} & {\bf req} 
\tabularnewline \hline \hline
 type  & label       & yes \\ \hline
 label & html text to display & yes
                      \\ \hline
\caption{Common keys for the 'params' section ({\em req} means required).}
\end{longtable}


\subsubsection{ \emph{readonly} type}

\begin{longtable}{|>{\bf}L{\dimexpr 0.27\linewidth}|L{\dimexpr 
0.58\linewidth}|c|}
\hline
 \centering {key}     & \centering {\bf description} & {\bf req} 
\tabularnewline \hline \hline
 type  & readonly    & yes \\ \hline
 label & description of the parameter & yes \\ \hline
 id         & parameter name in lowercase letters  & yes \\ \hline
 value\_expr & AngularJS expression used to compute the parameter value 
            & yes \\ \hline
\caption{Common keys for the 'params' section ({\em req} means required).}
\end{longtable}

\subsubsection{ \emph{checkbox} type}

\begin{longtable}{|>{\bf}L{\dimexpr 0.27\linewidth}|L{\dimexpr 
0.58\linewidth}|c|}
\hline
 \centering {key}     & \centering {\bf description} & {\bf req} 
\tabularnewline \hline \hline
 type  & checkbox  & yes \\ \hline
 label & description of the parameter or contents if type is label. & yes
                      \\ \hline
 id         & parameter name in lowercase letters  & yes \\ \hline
 default\_value & boolean: True for checked & \\ \hline
\caption{Common keys for the 'params' section ({\em req} means required).}
\end{longtable}

\subsubsection{ \emph{checkboxes} type}

\begin{longtable}{|>{\bf}L{\dimexpr 0.27\linewidth}|L{\dimexpr 
0.58\linewidth}|c|}
\hline
 \centering {key}     & \centering {\bf description} & {\bf req} 
\tabularnewline \hline \hline
 type  & checkboxes   & yes \\ \hline
 label & description of the parameter or contents if type is label. & yes
                      \\ \hline
 id         & parameter name in lowercase letters  & yes \\ \hline
 values     & list of dictionaries: [ {key:value, ...}, ... ]
            where key is the checkbox id and value is the text associated
            & yes \\ \hline
 default     & list of checkboxes that are checked by default  & yes \\ \hline
\caption{Common keys for the 'params' section ({\em req} means required).}
\end{longtable}


%-------------------------------------------------------------------------------
\subsection{The \emph{run} section}

In the command line, you can use \$param\_id to replace the to evaluate a 
python expression that can contain the parameter ids,
and '\textgreater output\_file' (without space between '\textgreater' and the 
filename) to redirect the standard output to a given file, save in the current 
working directory. 
If you also want to redirect the standard errors to the same file, use can add 
'2\textgreater\&1' as another argument. However, pipelines are not allowed 
('|' character).
Python scripts from the PythonTools directory can be used in commands.

\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
"run": [
  "nlmeans  input_0.sel.png $sigma input_1.png output_1.png",
  "img_diff input_0.sel.png input_1.png $sigma output_2.png",
  "img_mse  input_0.sel.png output_1.png >stdout.txt 2>&1"
]
\end{lstlisting}

%-------------------------------------------------------------------------------
\subsection{The \emph{config} section}

The config section is optional, it allows creating new (key,value) pairs in the 
configuration file based on text files obtained during the execution. This 
new information can then be used in the archive section.

\begin{longtable}{|>{\bf}L{\dimexpr 0.25\linewidth}|L{\dimexpr 0.6\linewidth}|c|}
\hline
\centering {key}     & \centering {\bf description} & {\bf req} \tabularnewline 
\hline \hline
 info\_from\_file    & it contains a list of (key,value) pairs where the key is
            the new information id to create (in lowercase letters) and the
            value is the corresponding text file that contains its contents & no \\ \hline
\caption{keys for the 'config' section.}
\end{longtable}

\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
"config":
  {
    "info_from_file": {  "homography_1" : "output_0.txt",
                          "homography_2" : "output_1.txt"
                      }
  }
\end{lstlisting}

%-------------------------------------------------------------------------------
\subsection{The \emph{archive} section}


\begin{longtable}{|>{\bf}L{\dimexpr 0.25\linewidth}|L{\dimexpr 0.6\linewidth}|c|}
\hline
\centering {key}     & \centering {\bf description} & {\bf req} \tabularnewline 
\hline \hline
 files    & (key,value) pairs where key is the file to archive and value is 
            the associated text information & no \\ \hline
 compressed\_\-files   & compressed files to add in the same format 
as files & no \\ \hline
 params  & list of parameters to archive & no \\ \hline
 info    & info variables to archive in the form of pairs variable:label & no \\ \hline
\caption{Keys for the 'text\_file' type.}
\end{longtable}


\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
"archive":
  {
    "files" : 
      { "input_0.png"                 : "input image",
        "primitives.txt"              : "Primitives"  },
    "params" :  
      [ "high_threshold_canny", 
        "initial_distortion_parameter", 
        "angle_point_orientation_max_difference" ],
    "info"   : { "run_time": "run time" }
  }
\end{lstlisting}

%-------------------------------------------------------------------------------
\subsection{The \emph{results} section}


The results section also contains an array of sets, where each each contains 
(key/value) pairs describing one type of output from the algorithm. There are 
displayed sequentially one below the other, a part from warnings that are 
displayed at the top of the page. The currently available types are described 
below. At the top of the results page, the processing time is displayed and the 
user is proposed to run the demo again with different input or parameters.


%------ gallery  ------
\subsubsection{ \emph{gallery} type}

The gallery type uses the gallery class to display images. Its parameters are:

\begin{longtable}{|>{\bf}L{\dimexpr 0.15\linewidth}|L{\dimexpr 0.7\linewidth}|c|}
\hline
 \centering {key}     & \centering {\bf description} & {\bf req} 
\tabularnewline \hline \hline
 type      & gallery  & yes \\ \hline
 label      & html label for the gallery, can be either a single string or 
             a list of string that will be concatenated with whitespace character
              in between & yes \\ \hline
 contents   & label:image\_filename pairs, if a filename does succeed in loading,
              the image will be removed from the gallery & yes \\ \hline
 style      & css style associated to the gallery, can contain Angular 
              expressions evaluated in the HTML template & yes \\ \hline
\caption{Keys for the 'gallery' type.}
\end{longtable}

\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
  {
    "type"          : "gallery",
    "label"         : "<h2>Resulting images</h2>",
    "contents"      : { 
      "Input"     : "input_0.sel.png", 
      "Output"    : "output.png"
    },
    "style"         : "height:{{sizeY*ZoomFactor}}px"
  },
\end{lstlisting}


%------ file_download  ------
\subsubsection{ \emph{file\_download} type}

\begin{longtable}{|>{\bf}L{\dimexpr 0.15\linewidth}|L{\dimexpr 0.7\linewidth}|c|}
\hline
\centering {key}     & \centering {\bf description} & {\bf req} \tabularnewline 
\hline \hline
 type      & file\_download  & yes \\ \hline
 label     & html title associated to the file download & yes \\ \hline
 contents  & either a single string of the filename to download, or a list
              of label:filename pairs for files to download & yes \\ \hline
\caption{Keys for the 'file\_download' type.}
\end{longtable}

\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
   {  "type"     : "file_download", 
      "label"    : "Download Hough result",
      "contents" : "output_hough.png" },
\end{lstlisting}

\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
    {
      "type"          : "file_download", 
      "label"         : "<h3>Download computed optical flow:</h3>",
      "contents"      : { "tiff": "stuff_tvl1.tiff", 
                          "flo" : "stuff_tvl1.flo",
                          "uv"  : "stuff_tvl1.uv" }
    },
\end{lstlisting}



%------ html_text  ------
\subsubsection{ \emph{html\_text} type}

\begin{longtable}{|>{\bf}L{\dimexpr 0.15\linewidth}|L{\dimexpr 0.7\linewidth}|c|}
\hline
\centering {key}     & \centering {\bf description} & {\bf req} \tabularnewline 
\hline \hline
 type      & html\_text  & yes \\ \hline
 contents   & & yes \\ \hline
\caption{Keys for the 'html\_text' type.}
\end{longtable}

\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
{ "type"     : "html_text", 
  "contents" : "Noise variance = {{params.anoise}}<br/>..."},
\end{lstlisting}


%------------ text_file --------------------------
\subsubsection{ \emph{text\_file} type}

\begin{longtable}{|>{\bf}L{\dimexpr 0.15\linewidth}|L{\dimexpr 0.7\linewidth}|c|}
\hline
\centering {key}     & \centering {\bf description} & {\bf req} \tabularnewline 
\hline \hline
 type      & text\_file  & yes \\ \hline
 label      & & yes \\ \hline
 contents   & & yes \\ \hline
 style      & & yes \\ \hline
\caption{Keys for the 'text\_file' type.}
\end{longtable}

\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
{  "type"     : "text_file", 
  "label"    : "<h2>Additional info<h2>",
  "contents" : "output.txt",
  "style"    : "width:{{sizeX}}px;height:14em" },
\end{lstlisting}

%------ warning  ------
\subsubsection{ \emph{warning} type}

\begin{longtable}{|>{\bf}L{\dimexpr 0.15\linewidth}|L{\dimexpr 
0.7\linewidth}|c|}
\hline
 \centering {key}     & \centering {\bf description} & {\bf req} 
\tabularnewline \hline \hline
 type      & warning  & yes \\ \hline
 condition & warning condition evaluated by AngularJS in its 
the context of the result controler named {\em DemoResultCtrl}. In this 
context, the user has access, among other variables, to: -'demo' which 
contains the demo description, - 'params' which contains the current 
values of all the parameters, - sizeX and sizeY as the input image dimensions.  
& yes \\ \hline
 contents  & displayed text, can contain both HTML tags and AngularJS 
expressions of the form '\{\{expression\}\}'. & \\ \hline
\caption{Keys for the 'warning' type.}
\end{longtable}

\paragraph{Example}:\\

\begin{lstlisting}[language=json,firstnumber=1]
{ "type":"warning", 
  "condition":"sizeX * sizeY < X",
  "contents":"Needs X pixels ({{sizeX *sizeY}} given)<br/>"},
\end{lstlisting}


\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
{ "type"     : "gallery",
  "label"    : "<h3>Images</h3>",
  "contents" : {"Input":"input.png", "Output":"output.png"},
  "style"    : "width:{{sizeY}}px" },
\end{lstlisting}

%------ repeat_gallery  ------
\subsubsection{ \emph{repeat\_gallery} type}
The repeat\_gallery type is design to display a gallery with a number of images 
that depend on a parameter, for example the number of scales used by the 
algorithm.

\begin{longtable}{|>{\bf}L{\dimexpr 0.15\linewidth}|L{\dimexpr 0.7\linewidth}|c|}
\hline
\centering {key}     & \centering {\bf description} & {\bf req} \tabularnewline 
\hline \hline
 type      & repeat\_gallery  & yes \\ \hline
 label      & & yes \\ \hline
 repeat     & & yes \\ \hline
 contents   & & yes \\ \hline
 style      & & yes \\ \hline
\caption{Keys for the 'repeat\_gallery' type.}
\end{longtable}

\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
{ "type"     : "repeat_gallery",
  "repeat"   : "params.scales",
  "label"    : "<h2> Noise Curves </h2>",
  "contents" : [ "Scale {{idx}}: curve_{{idx}}.png"],
  "style"    : "height:600px" },
\end{lstlisting}

\paragraph{Example}:\\
\begin{lstlisting}[language=json,firstnumber=1]
{ "type"     : "repeat_gallery",
  "repeat"   : "params.scales",
  "label"    : "<h2> Noise Curves </h2>",
  "contents" : [ "Scale {{idx}}: curve_{{idx}}.png"],
  "style"    : "height:600px" },
\end{lstlisting}

%-------------------------------------------------------------------------------
\subsection{Full examples}


\subsubsection{keywords}

\section{AngularJS components}
\subsection{Services}
\subsection{Controlers}
\subsection{Templates}
