% Instructions to modify this document:
% * Remember to ALWAYS execute "git pull" BEFORE any commit you make!
% * Use the \ToDo{...} command to remark tasks which still need to be done. Add your name in the comment.
% * Use the \input{file.tex} command to split the document into several parts
% * Do not change the current LaTeX coding style to yours. The style and format should be homogeneous along sections.

% To convert .dia diagrams into PDF:
% 1) Create the diagram with dia (or any other tool)
% 2) Export it as .eps
% 3) use epstopdf to convert to PDF


\documentclass[a4paper,12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{amsmath,graphicx}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{subfigure}
\usepackage{ifpdf}
\usepackage{url}
\usepackage{color}
\usepackage[hidelinks]{hyperref}
\usepackage{multirow}
\usepackage{datetime}
\usepackage{comment}
\usepackage{float} % To put figures in their exact place with \begin{figure}[H]
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{xcolor}


\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}


% Definitions and commands
\def \np{\vskip 0.25 cm}
\def \ap{\vskip 0.15 cm}

% JSON listing (see 
%  http://tex.stackexchange.com/questions/83085/how-to-improve-listings-display 
% -of- json-files)
\colorlet{punct}{red!60!black}
\definecolor{background}{HTML}{EEEEEE}
\definecolor{delim}{RGB}{20,105,176}
\colorlet{numb}{magenta!60!black}

\lstdefinelanguage{json}{
    basicstyle=\footnotesize\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{background},
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}
      {]}{{{\color{delim}{]}}}}{1},
}


\newcommand{\ToDo}[1]{\textcolor{magenta}{\textbf{[ToDo]} \textbf{#1}}}


\begin{document}


\begin{titlepage}

\begin{center}
\vspace*{-1in}

\vspace*{0.6in}
\begin{Large}
\textbf{The IPOL Demo System 2.0 \\Technical documentation} \\
\end{Large}

\vspace*{0.6in}

\small{Compiled on \today\ at \currenttime}

\vspace*{0.6in}
\rule{80mm}{0.1mm}\\
\vspace*{0.1in}
\end{center}

\end{titlepage}

This document contains technical documentation for the IPOL Demo System 2.0. Specifically, the architecture of the service-oriented platform, its modules, and the real-time template generation of demos from their textual description.
\vspace*{0.6in}

\textbf{Project direction and team coordination}

Miguel Colom - \url{http://mcolom.info}

\vspace*{0.2in}

\textbf{Software engineers and external consultats, past and present (in alphabetical order):}


José Arrecio

Miguel Colom

Vincent Firmin

Karl Krissian

Alexis Mongin

Nelson Monzón


%\maketitle
\newpage

\tableofcontents
\newpage
\listoffigures
\newpage

% The Archive module
\input{introduction/introduction.tex}

% The Core
\input{core/core.tex}

% The Proxy module
\input{proxy/proxy.tex}

% The Blobs module
\input{blobs/blobs.tex}

% The Archive module
\input{archive/archive.tex}

% The Demo Info module
\input{demo_info/demo_info.tex}
\ToDo{Secure access to Ws, oauth perhaps?}

% The Demo Dispatcher module
\input{demo_dispatcher/demo_dispatcher.tex}

% The Demo Runner module
\input{demo_runner/demo_runner.tex}

% The Control Terminal 
\input{terminal/terminal.tex}



\section{System administration}
\ToDo{This section is just a stub for the moment. Add all the system administration and configuration stuff here}

- Backups. For the moment we use the very simple script at {\tt ipolDevel/sysadmin/backup.sh}
Cron controls it. To add the cron line, use {\tt crontab -e} as root.

For example, to run the backup script once per week at 3:00h, add this line:

{\tt 0 3 * * 1 /home/ipol/ipolDevel/sysadmin/backup.sh}

- Cleanup. The script {\tt ipolDevel/sysadmin/backup.sh} does a cleanup of all temporary files older than one month. To execute each month, the following line needs to be added with {\tt crontab -e} as root.

{\tt 0 5 * * 1 /home/ipol/ipolDevel/sysadmin/cleanup.sh}


\subsection{GitHub deploy key}
The IPOL GitHub repository might be private. Thus, is any server needs to obtain the complete source code of the demo system, a \emph{deploy key} is needed. The deploy key is added to the GitHub configuration and each server needs to get the sources using the deploy key.

For example:

\begin{verbatim}
ipol@smartalgo:~/ipolDevel$ cat ~/.ssh/config 
host github_deploy
      hostname github.com
      user git
      identityfile ~/.ssh/id_rsa
\end{verbatim}

\vspace{0.15cm}

\begin{verbatim}
ipol@smartalgo:~/ipolDevel$ cat ~/.ssh/config 
host github_deploy
      hostname github.com
      user git
      identityfile ~/.ssh/id_rsa

ipol@smartalgo:~/ipolDevel$ cat .git/config 
[core]
	repositoryformatversion = 0
	filemode = true
	bare = false
	logallrefupdates = true
[remote "origin"]
	#url = https://github.com/mcolom/ipolDevel
	url = git@github_deploy:mcolom/ipolDevel.git
	fetch = +refs/heads/*:refs/remotes/origin/*
[branch "master"]
	remote = origin
	merge = refs/heads/master
\end{verbatim}

We use the host \emph{github\_deploy} in order to pick the deploy key in the SSH connection.

\subsection{Setup of a new machine}
When a new machine is added to the IPOL infrastructure, the following needs to be done:
- Create the {\tt ipol} user in a new machine: {\tt adduser --disabled-password ipol}

- Install bash-completion {\tt apt-get install bash-completion}

- Install cron-apt: {\tt apt-get install cron-apt}

And edit /etc/cron-apt/config:
\begin{verbatim}
APTCOMMAND=/usr/bin/apt-get
OPTIONS="-o quiet=1 -o Dir::Etc::SourceList=/etc/sources.list"
SYSLOGON="always"
\end{verbatim}

- Configuration of the email server to be able to send emails form any of the IPOL servers: configure with {\tt dpkg-reconfigure exim4-config} and be sure to choose the option to send email on the Internet, not local.

Install mail with {\tt apt-get install mailutils}

To send an email: {\tt cat email.txt | mail -s "This is the subject" john.doe@example.com,banania.guy@example.com}


- Setup priorities and memory limits to the processes of the users.

Added this to /etc/security/limits.conf:
\begin{verbatim}
*               soft     priority            17
ipol            soft     priority            0
\end{verbatim}

We need to set also limits for the memory usage per user. It'd be great if we could do it as a percentage of the free memory.


%To limit the memory which a group of users can use, we should use {\tt cgroups} along with the {\tt Cgred} daemon.
%
%More info:
%
%\url{https://www.digitalocean.com/community/tutorials/how-to-limit-resources-using-cgroups-on-centos-6}
%
%\url{https://access.redhat.com/documentation/en-US/Red_Hat_Enterprise_Linux/6/html/Resource_Management_Guide/sec-Moving_a_Process_to_a_Control_Group.html}



\section{General notes}
In this section we add general comments on the projects, parts which still neeed to be written or coded. In general, information which needs to be documented but has not still found its place in the document. It works as a reminder not to forget.

\begin{itemize}
  \item The magic module. We use PIP, not the python-magic package found in most distributions. \ToDo{Explain why}.
  \item List of packages needed and how to install them.
  \item Description of the general requirements needed for a module to be part of the system (start, ping, and shutdown services ; structure of the general launching script...
\end{itemize}

- List of packages used for installing the system. Packages to be installed with sudo apt-get install:

\begin{itemize}
\item python2.7
\item wget: to download files
\item cmake: to create a multiplatform Makefile easily
\item libtiff5-dev, libjpeg-dev, libpng-dev: open and write TIFF, JPEG, PNG files
\item libfftw3-dev: fast DFT operations
\item libgsl0-dev, libeigen3-dev, liblapack-dev, libblas-dev: linear algebra
\item python, python-dev, python-cherrypy3, python-mako, python-jsonschema: Python language, Python headers, webserver, web templating, JSON
\item gnuplot, gnuplot-nox: to draw figures
\item python-pip: to install python packages
\item python-yaml: for parsing
\item libpq-dev: PostgreSQL headers
\item libmagic-dev: needed to install python-magic with pip
\item libav-tools: audio/video tools for demos with these data types
\end{itemize}
Packages to be installed with pip install:
\begin{itemize}
\item python-magic
\item pillow
\item simplejson
\end{itemize}

- Example of another demo system: \url{http://places.csail.mit.edu/demo.html}

- Integrate Openseedragon, \url{https://openseadragon.github.io/}

- Document the format of the demo package, with desc.jon, images/, extra/, etc

- Most of our modules name the files according to the hash sum of their contents. This file names are OK for internal use, but the users should obtain the files with the proper names. This can be achieved with the ``download" attribute in HTML5. All website interfaces should provide the corresponding human-readable name. For example:

\begin{verbatim}
<a href="9021384984901238490128490123841222223312.png" download="denoised.png">
  Download the denoised image
</a>
\end{verbatim}

- Look for potential race conditions everywhere in the code, specially at the modules. Use locks to prevent them.

- All webservices should return a \emph{status:KO} when they fail. For example, if they're asked a service which doesn't exist they should return the status:KO, but never simply return a cherrypy message because of an untreated exception. Example of a wrong behavior:

\begin{verbatim}
http://ns3018037.ip-151-80-24.eu:9002/hello

404 Not Found

The path '/hello' was not found.

Traceback (most recent call last):
  File "/usr/lib/python2.7/dist-packages/cherrypy/_cprequest.py", line 670, in respond
    response.body = self.handler()
  File "/usr/lib/python2.7/dist-packages/cherrypy/lib/encoding.py", line 217, in __call__
    self.body = self.oldhandler(*args, **kwargs)
  File "/usr/lib/python2.7/dist-packages/cherrypy/_cperror.py", line 411, in __call__
    raise self
NotFound: (404, "The path '/hello' was not found.")
Powered by CherryPy 3.5.0
\end{verbatim}

- In general, check that no FK reference is missing at any of the database schemas of the modules, and that they're correct.
Also, we need to check absolutely that all the CASCADE DELETE are correct!

- FYI: the package \emph{sqlitebrowser} seems to be a very good tool to browse and develop the SQLite schemas.

- The demoInfo module returns \emph{Content-Type: text/html} instead of application/json:

\begin{verbatim}
curl --head http://ns3018037.ip-151-80-24.eu:9002/read_demo_description?demodescriptionID=359
HTTP/1.1 200 OK
Date: Sun, 21 Feb 2016 19:41:29 GMT
Content-Length: 3545
Content-Type: text/html;charset=utf-8
Server: CherryPy/3.5.0
\end{verbatim}
\ToDo{Check that all modules return application/json and Content-Type: text/json;charset=utf-8}

Also, this module returns a JSON which contains a lots of backslashes!:

\begin{verbatim}
curl "http://ns3018037.ip-151-80-24.eu:9002/read_demo_description?demodescriptionID=359"

{"status": "OK", "demo_description": "\"{\\\"archive\\\": {\\\"files\\\": {\\\"diffInputIHS.png\\\":
\\\"difference input-IHS\\\", \\\"diffInputPanS.png\\\": \\\"difference input-pansharpened\\\",
\\\"ihs.png\\\": \\\"IHS image\\\", \\\"input_0.sel.png\\\": \\\"input image\\\",
\\\"lowspectral.png\\\": \\\"lowspectral image\\\", \\\"pan.png\\\": \\\"pan image\\\",
\\\"pansharpened.png\\\": \\\"pansharpened image\\\"}, \\\"params\\\": [\\\"sfactor\\\"]},
\\\"build\\\": [{\\\"binaries\\\": [[\\\".\\\", \\\"pansharpening_ipol\\\"],
\end{verbatim}

This is clearly wrong. Compare with
\begin{verbatim}
curl "http://api.flickr.com/services/feeds/photos_public.gne?format=json"

sonFlickrFeed({
                "title": "Uploads from everyone",
                "link": "http://www.flickr.com/photos/",
                "description": "",
                "modified": "2016-02-21T19:58:40Z",
                "generator": "http://www.flickr.com/",
                "items": [
           {
                        "title": "P5302235",
                        "link": "http://www.flickr.com/photos/lievensoete/245457
53194/",
...
\end{verbatim}
\ToDo{Correct demoInfo so it returns a correct JSON response}

- A way to get images from the browser in a smartphone with HTML5: \url{http://don.github.io/html-cam/}


\ToDo{Keep adding!}

\subsection{Git branches}
There are two git branches:

\begin{itemize}
  \item \textbf{master}: development
  \item \textbf{prod}: production
\end{itemize}

The {\tt master} branch is the default, where all development contributions are made. The testing server is configured to fetch this branch.

The {\tt prod} branch is for production. It is merged with {\tt master} only when the master is stable and one wants to integrate the changes in production. The production servers fetch this branch.

The {\tt prod} branch was created with:
\begin{verbatim}
git checkout -b prod
git push --set-upstream origin prod
\end{verbatim}

The .git/config ends up as:

\begin{verbatim}
[core]
	repositoryformatversion = 0
	filemode = true
	bare = false
	logallrefupdates = true
[remote "origin"]
	url = git@github.com:mcolom/ipolDevel.git
	fetch = +refs/heads/*:refs/remotes/origin/*
[branch "master"]
	remote = origin
	merge = refs/heads/master
[branch "prod"]
	remote = origin
	merge = refs/heads/prod
\end{verbatim}

To merge {\tt prod} with {\tt master:}
\begin{verbatim}
git checkout prod
git merge master
git push
git checkout master
\end{verbatim}


\section{To Do}
- Automatic testing. Two kind of tests:
\begin{itemize}
  \item For the IPOL system itself
  \item To ensure good compilation of the algorithm source codes
\end{itemize}

We need to use PyUnit for the unit tests.

- Implement authentication in the Proxy to prevent that unauthorized entities (i.e. other that the CP) perform write operations in the system. It can be done for example with a service in the Proxy which add the client to a table of authorized clients for some time, and a list of privileged functions in the API.

- Add statistics data collecting. Piwik can be used for this.


\bibliographystyle{plain}
\bibliography{biblio}

\end{document}
% End of document

