\subsection{Demo copy script}

The demo copy script is a tool that allows to clone a demo from one environment to another. This tool is useful for development purposes
as it allows a developer to quickly clone a demo to a local environment. The only parameter is the demo ID number in order to copy
everything related to the demo, this includes the DDL, it's demo extras file, the blobs associated to the demo, and it's templates.

\subsubsection{Usage}
This script is developed using python 3 so in order to use the script, it will need to use the correct version. By default, the script gets
the demo information from the production environment. If the demo to be copied is in the integration environment there is an argument
(-i) which allows to set the source environment to integration.
It will also check if there is a demo with the provided ID number and ask for another one in case it's appropriate to choose
a new one or overwrite the demo. If a demo with the same title already exists the script will ask for a new one.

\paragraph{Copy demo from production environment} \hspace{0pt} \\
python3 demo\_copy.py {\tt <demo\_id>}

By default it will use production environment as a source.

\paragraph{Copy demo from integration environment} \hspace{0pt} \\
python3 demo\_copy.py -i {\tt <demo\_id>}

With the argument -i it will use integration environment as a source.

\paragraph{Copy demo from integration environment} \hspace{0pt} \\
python3 demo\_copy.py -h

It prints the script help information.

